Deep Learning

### 2015-01-12 deepreview.tex
added the tricks of the trade book citation

%%%%%%% GEOFF %%%%%%%%%%
%GEOFF: Do box explaining backprop equatons
%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\includegraphics[width=0.33\linewidth]{chain-rule.pdf}
\includegraphics[width=0.33\linewidth]{forward-graph.pdf}
\includegraphics[width=0.33\linewidth]{backward-graph.pdf}
}
\caption{
Left: the chain rule of derivatives tells us how
two small effects (that of a small change of $x$ on $y$, and that of $y$ on $z$)
are composed. A small change $\Delta x$ in $x$
gets transformed first into a small change $\Delta y$ in $y$
by getting multiplied by $\frac{\partial y}{\partial x}$
(that is the definition of partial derivative). Similarly
that creates a change $\Delta z$ in $z$. Inserting one equation
into the other gives the chain rule of derivatives, i.e., how
$\Delta x$ gets turned into $\Delta z$ through multiplication
by the product of $\frac{\partial y}{\partial x}$ and
$\frac{\partial z}{\partial x}$. It also works when $x$, $y$
and $z$ are vectors (and the derivatives are Jacobian matrices). \newline
Middle: many computations, such as the succession of linear and non-linear 
transformations of multi-layer neural networks, can be described as
a graph where each node $i$ computes a quantity $u_i$ (e.g. the
output of an artificial neuron or the value of a parameter such as
a synaptic weight), based on the set of values $a_i$, composed of elements $u_j$ of
predecessors in the graph, i.e., $u_i = f_i(a_i)$. \newline
Right: the chain rule can be generalized to such computational
flow graphs by recursively computing the derivative of the final
node $u_N$ (e.g., the error to be minimized or the output of the neural network)
with respect to every internal node. The basic recursive equation
is
$\frac{\partial u_N}{\partial u_j} = \sum_{i: j \in a_i} \frac{\partial u_N}{\partial u_i}
\frac{\partial f(a_i)}{\partial u_j}.$
}
\end{minipage}
}
\label{fig:backprop-box}
\end{figure}

@@

Backpropagation provides an efficient way of computing gradients with respect to all of
the weights in a layered network on a single training case, but there are
still many ways to make use of these gradients. The most obvious method is
to average the gradients over all of the cases in the training set and then
to change each weight in proportion to its negative gradient, which is the
direction where a small change will most improve the objective function. 
When the training set contains millions of cases and is highly redundant
% explaining what ``redundant'' means, here
(with many examples illustrating variations of the the same underlying 
aspect or concept), however,
this is needlessly slow. It is much faster to compute the average gradient
on a small ``mini-batch'' of randomly chosen training cases and to update
each weight by this stochastic estimate of its full gradient times a
learning rate which decays as learning proceeds. Stochastic gradient
descent can be improved by using the history of the individual weight
gradients to adapt the learning rate for each weight~\citep{bottou-bousquet-2008-small}
or to provide additional increments that depend on earlier gradients~\citep{momentum}
but these techniques are still the subject of controversy and are beyond
the scope of this review.  However, it is now widely accepted that some
form of stochastic gradient descent is the best bet for large, redundant
datasets.

>>>>

%%%%%%% GEOFF %%%%%%%%%%
%GEOFF: Do box explaining backprop equatons
%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\includegraphics[width=0.33\linewidth]{chain-rule.pdf}
\includegraphics[width=0.33\linewidth]{forward-graph.pdf}
\includegraphics[width=0.33\linewidth]{backward-graph.pdf}
}
\caption{
Left: the chain rule of derivatives tells us how
two small effects (that of a small change of $x$ on $y$, and that of $y$ on $z$)
are composed. A small change $\Delta x$ in $x$
gets transformed first into a small change $\Delta y$ in $y$
by getting multiplied by $\frac{\partial y}{\partial x}$
(that is the definition of partial derivative). Similarly,
the change $\Delta y$ creates a change $\Delta z$ in $z$. Substituting one equation
into the other gives the chain rule of derivatives, i.e., how
$\Delta x$ gets turned into $\Delta z$ through multiplication
by the product of $\frac{\partial y}{\partial x}$ and
$\frac{\partial z}{\partial x}$. It also works when $x$, $y$
and $z$ are vectors (and the derivatives are Jacobian matrices). \newline
Middle: many computations, such as the succession of linear and non-linear 
transformations of multi-layer neural networks, can be described as
a graph where each node $i$ computes a quantity $u_i$ (e.g. the
output of an artificial neuron or the value of a parameter such as
a synaptic weight), based on the set of values $a_i$, composed of elements $u_j$ of
predecessors in the graph, i.e., $u_i = f_i(a_i)$. This can be readily
generalized to nodes whose output is a vector or a matrix.\newline
Right: the chain rule can be applied efficiently to computational
flow graphs by recursively computing the derivative of the final
node $u_N$ (e.g., the error to be minimized or the output of the neural network)
with respect to every internal node. The basic recursive equation
is
$\frac{\partial u_N}{\partial u_j} = \sum_{i: j \in a_i} \frac{\partial u_N}{\partial u_i}
\frac{\partial f(a_i)}{\partial u_j}.$
}
\end{minipage}
}
\label{fig:backprop-box}
\end{figure}

@@

Backpropagation provides an efficient way of computing gradients with respect to all of
the weights in a layered network on a single training case, but there are
still many ways to make use of these gradients. The most obvious method is
to average the gradients over all of the cases in the training set and then
to change each weight in proportion to its negative gradient, which is the
direction where a small change will most improve the objective function. 
When the training set contains millions of cases and is highly redundant
% explaining what ``redundant'' means, here
(with many examples illustrating variations of the same underlying 
aspect or concept), however,
this is needlessly slow. It is much faster to compute the average gradient
on a small ``mini-batch'' of randomly chosen training cases and to update
each weight by this stochastic estimate of its full gradient, times a
learning rate which decays as learning proceeds. Stochastic gradient
descent can be improved by using the history of the individual weight
gradients to adapt the learning rate for each weight~\citep{bottou-bousquet-2008-small}
or to provide additional increments that depend on earlier gradients~\citep{momentum}
but these techniques are still the subject of controversy and are beyond
the scope of this review (but see~\citet{Montavon2012} for tricks of the trade). 
However, it is now widely accepted that some
form of stochastic gradient descent is the best bet for large, redundant
datasets.
